---
title: "Using Leaflet"
output:
  html_document:
    df_print: paged
---

## Using Leaflet for map generation
```{r}
library(leaflet)
my_map <- leaflet() %>% ##piping notation simply adds additional functions/arguments to my_map output. Helps reduce time
  addTiles()  ##adds first set of content
my_map
```


## Adding markers to a map
```{r}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=39.2980803, lng=-76.5898801, 
             popup="Jeff Leek's Office")
my_map
```

## Adding multiple markers

Adding one marker at a time is often not practical if you
want to display many markers. If you have a data frame with
columns `lat` and `lng` you can pipe that data frame into
`leaflet()` to add all the points at once.
```{r}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 39.2, max = 39.3), ## here we could import read.csv any file that has this info
                 lng = runif(20, min = -76.6, max = -76.5))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```

## Making custom markers for your map

The blue markers that leaflet comes packaged with may not be
enough depending on what you're mapping. Thankfully you can
make your own markers from `.png` files.
```{r}
hopkinsIcon <- makeIcon(
  iconUrl = "http://brand.jhu.edu/content/uploads/2014/06/university.shield.small_.blue_.png",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)
hopkinsLatLong <- data.frame(
  lat = c(39.2973166, 39.3288851, 39.2906617),
  lng = c(-76.5929798, -76.6206598, -76.5469683))
hopkinsLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hopkinsIcon)
```

## Mapping clusters of markers

Sometimes you might have so many points on a map that it
doesn't make sense to plot every marker. In these situations
leaflet allows you to plot clusters of markers using
`addMarkers(clusterOptions = markerClusterOptions())`. When
you zoom in to each cluster, the clusters will separate until
you can see the individual markers.
```{r}
df <- data.frame(lat = runif(500, min = 39.25, max = 39.35),
                 lng = runif(500, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```

## Mapping circle markers
```{r}
df <- data.frame(lat = runif(20, min = 39.25, max = 39.35),
                 lng = runif(20, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers()
  

```

## Drawing circles that change based on variable input
```{r}
md_cities <- data.frame(name = c("Baltimore", "Frederick", "Rockville", "Gaithersburg", 
                                 "Bowie", "Hagerstown", "Annapolis", "College Park", "Salisbury", "Laurel"),
                        pop = c(619493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346),
                        lat = c(39.2920592, 39.4143921, 39.0840, 39.1434, 39.0068, 39.6418, 38.9784, 38.9897, 38.3607, 39.0993),
                        lng = c(-76.6077852, -77.4204875, -77.1528, -77.2014, -76.7791, -77.7200, -76.4922, -76.9378, -75.5994, -76.8483))
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)
```

