---
title: "Presenting Using R_Markdown"
author: "Alex P"
date: "2022-11-14"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Two pound signs are what create a new slide (with title)
Some content here- this is plain text

*this is italicized text*

**this is bold text**



*** 
### This is a top level subheading
#### Second level subheading


This is a new slide without a title



## R Markdown

This is an R Markdown presentation. 

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Things we wish to consider are the following:
  - version controlling a presentation
  - Reproducibility
  - Ability to share across platforms (i.e. everyone has a web browser)
  - Ease of creating
  
  1. item 1 for ordered list
  2. item 2 for ordered list

## Summarizing the Diamond dataset

```{r cars, echo = FALSE, comment=""}
## above, the comment = "" blank takes away the first "column" from the data.frame
library(ggplot2)
d1 <-diamonds[ ,1:4]
head(d1)
summary(d1)
```

## Diamond data using Plotly

```{r byFormat, echo = FALSE, message=FALSE, warning= FALSE, fig.width= 7, fig.height=5}
library(plotly)
library(ggplot2)
set.seed(100)
d <- diamonds[sample(nrow(diamonds),1000), ]

p <- ggplot(data = d, aes(x = carat, y = price)) +
  geom_point(aes(text = paste("Clarity:", clarity)), size = 4) +
  geom_smooth(aes(color = cut, fill = cut)) +
  facet_wrap(~ cut)
  

(gg <- ggplotly(p))  ##how to make any ggplot interactive using plotly.

```

